Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-06-06 docs/00-manuscripts/ieee/ieee-manuscript.tex
typo
remove unnecessary sentence
remove "almost"

% - Ensemble FS shows no advantage to simple methods -> always one simple filter which is better. Ensemble filters are good across many different datasets
The models which used the Borda ensemble method in this study did not score better on average than models which used a single filter or no filter at all.
Ensemble methods have higher stability and robustness than single ones and have shown promising results in \cite{drotar2017a}.
Hence, their main advantage are stable performances across datasets with varying characteristics.
Single filter methods might yield better model performances on certain datasets but fail on others.
The fact that this study used multiple feature sets but only one dataset and tested many single filters could be a potential explanation why in all cases (besides RF on task HR-NRI-VI) a single filter outperformed the ensemble filter.
However, studies which used ensemble filters are still rare and usually these are not compared against single filters \cite{ghosh2019}.
In summary, Borda performs no better than a randomly selected filter method in this study.
More case studies applying ensemble filter methods are needed to verify this finding.
Nevertheless, ensemble filters can be a promising addition to a ML feature-selection portfolio.

@@

Environmental datasets always come with some constraints that can have potential influence on the modeling process and its outcome.
The following paragraph discusses these.

Finding a suitable approach to extract the remote sensing information from each tree was a complex process.
Due to the reported geometric offset of up to one meter within the hyperspectral data, the risk of assigning a value to an observation which would actually refer to a different, possibly non-tree, pixel was reasonably high.
It was concluded that using a buffer of one meter can be a good compromise between the inclusion of information from too many surrounding trees, mapping a single tree crown accordingly accounting for a possible geometric offset.
The applied buffer only included a pixel value if the distance to the centroid of a pixel was smaller than the buffer radius (i.e. <= 1m).
This results in almost all cases in four contributing pixels (= four square meters) for the extraction of hyperspectral information for a given tree.
Even though no results showing the influence of different buffer values on the extraction were provided, it is hypothesized that the relationships between features would not change substantially, leading to almost identical model results.
Besides using a buffer to extract the hyperspectral information, a segmentation could have been considered.
However, this method would have required more effort for no clear added value in our view and would have moved the focus of this manuscript more to data preprocessing and away from the focus on filter-based feature selection methods.

>>>>

% - Ensemble FS shows no advantage to simple methods -> always one simple filter which is better. Ensemble filters are good across many different datasets
The models which used the Borda ensemble method in this study did not score better on average than models which used a single filter or no filter at all.
Ensemble methods have higher stability and robustness than single ones and have shown promising results in \cite{drotar2017a}.
Hence, their main advantage are stable performances across datasets with varying characteristics.
Single filter methods might yield better model performances on certain datasets but fail on others.
The fact that this study used multiple feature sets but only one dataset and tested many single filters could be a potential explanation why in all cases (besides RF on task HR-NRI-VI) a single filter outperformed the ensemble filter.
However, studies which used ensemble filters are still rare and usually these are not compared against single filters \cite{ghosh2019}.
In summary, Borda performs not better than a randomly selected filter method in this study.
More case studies applying ensemble filter methods are needed to verify this finding.
Nevertheless, ensemble filters can be a promising addition to a ML feature-selection portfolio.

@@

Environmental datasets always come with some constraints that can have potential influence on the modeling process and its outcome.
Finding a suitable approach to extract the remote sensing information from each tree was a complex process.
Due to the reported geometric offset of up to one meter within the hyperspectral data, the risk of assigning a value to an observation which would actually refer to a different, possibly non-tree, pixel was reasonably high.
It was concluded that using a buffer of one meter can be a good compromise between the inclusion of information from too many surrounding trees, mapping a single tree crown accordingly accounting for a possible geometric offset.
The applied buffer only included a pixel value if the distance to the centroid of a pixel was smaller than the buffer radius (i.e. <= 1m).
This results in all cases in four contributing pixels (= four square meters) for the extraction of hyperspectral information for a given tree.
Even though no results showing the influence of different buffer values on the extraction were provided, it is hypothesized that the relationships between features would not change substantially, leading to almost identical model results.
Besides using a buffer to extract the hyperspectral information, a segmentation could have been considered.
However, this method would have required more effort for no clear added value in our view and would have moved the focus of this manuscript more to data preprocessing and away from the focus on filter-based feature selection methods.
